\documentclass{article}
\usepackage{enumitem,amssymb}
\newlist{todolist}{itemize}{2}
\setlist[todolist]{label=$\square$}
\usepackage{pifont}
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%
\newcommand{\done}{\rlap{$\square$}{\raisebox{2pt}{\large\hspace{1pt}\cmark}}%
\hspace{-2.5pt}}
\newcommand{\wontfix}{\rlap{$\square$}{\large\hspace{1pt}\xmark}}

\title{To-Do}
\author{Leopold Ingenohl}


\begin{document}
\maketitle


  \begin{todolist}
  \item[\done] Frame the problem
  \end{todolist}

\begin{todolist}

  \item Print Components and Kube Mail 
  \item How can we compare the financial strength of the investor with that of the target?
  \item Literature on signs for a takeover
  \item Motivation of the investor - studies?
  \item Topics: Conglomerate Discount, Asymmetric Information
  \item Read a few SC13D filings of the sample to understand what is going on
  \item Preparation of the final sample (all further analysis will be based on it)


\end{todolist}

\section{Main objective of the paper}

  \begin{center}
    Examining the link between the financial condition of the investor and the subsequent abnormal returns on the targets stock.
  \end{center}

  \subsection{Investors}
    
    \begin{enumerate}

      \item Determine abnormal returns with respect to the selected sample 

      \item Ranking/grouping of investors by their financial strength/condition. 

      \item Grouping of returns by financial strength of the investor.

      \item Cross-sectional regression of financial strength components with regards to the returns
    \end{enumerate}

  \subsection{Target}

    \begin{enumerate}

      \item Characteristics of the target 
      \item Similar to the methodology applied to the investor
    \end{enumerate}

  \subsection{Investor-Target relation}

    \begin{enumerate}
      \item Industries
      \item Comparison of financial conditions 
      \item Grouping the returns with regards to the above factors
    \end{enumerate}

\section{Preparation of the base sample}

  \begin{enumerate}
    \item SC 13D \& SC 13D/A Filings? 
    \item Period
    \item Sample of all filings
    \item Filter with 10k reports 
    \item CRSP share code http://www.crsp.com/products/documentation/data-definitions-1
    Share Code: First Digit: 1 = Ordinary Common shares, 3 = ADR, 4 = Shares of Beneficial Interest, 7 = Unit or Limited Partnership. Second Digit: 0 = No special status found, 1 = No special status necessary, 2 = Foreign incorporated, 4 = Closed End Fund, 8 = REIT	
    \item COMPUSTAT \& CRSP Data availability
    \item Manual Selection
  \end{enumerate}

\section{Activism}

  \begin{enumerate}
    \item No institutional investor activism but 
    \item effecting a major change in the company 
  \end{enumerate}

\section{Expected Return Proxy}

  \begin{enumerate}
    \item The accounting fundamentals used as explanatory variables in the proxies for expected profitability and investment include lagged values of Bt/Mt, a dummy variable for negative earnings, profitability (Yt/Bt) for firms with positive earnings, accruals relative to book
    equity for firms with positive (+ACt/Bt) and negative (ACt/Bt) accruals, investment (dAt/At?1), a dummy variable for firms that do not pay dividends (No Dt) and the ratio of dividends to book equity (Dt/Bt).{Fama2006}

    \item What is the result of the calculation?! 
    \item read paper again 
  \end{enumerate}

\section{Identifying Information}

\begin{enumerate}
  \item GIC variables - will merge them with the current sample - based on the PERMCO and CIK 
  \item Those the right ones? 
  \item NAICS, GIC or SIC
\end{enumerate}

\section{Cross-Section Regression}

\begin{enumerate}
  \item Dummy variables 
  \item year, industry, strength etc. 
\end{enumerate}

\section{title}
\end{document}